Differential Expression - HBCC - sgACC - Dx

### 2020-05-20 individual-cohorts/HBCC_sgACC_DE.Rmd
fix dream input? did not fail in other cohorts

# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION,
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

>>>>

# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION$E,
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)
